### 2015-08-30 trunk/doc/plan.tex
Update to SCM plan
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2724 40876441-3496-0410-a613-a2fca35b2ae2

This section contains information on the \textit{Software Configuration
Management Plan} for the \textit{Ludwig} code.
It is to provide users of the code a background on the way in which
the code is developed, how bugs are dealt with, the way in which
new features may be added, and so on. It is therefore a part
of the process by which the code is maintained. The Software Configuration
Management Plan will be referred to as `The Plan' throughout the remainder
of the section.

@@

The \textit{Ludwig} code is designed to study the hydrodynamic properties
of simple and complex fluids based around the numerical solution of the
Navier-Stokes equations. Complex fluids are dealt with via a free-energy
based finite difference approach, which couples explicitly to the
hydrodynamics. Examples of complex fluids include binary mixtures,
surfactants, liquid crystals, and active gels. Solid objects such as
porous media may be included, as well as moving particles (colloids).
Components of \textit{Ludwig} include the main program, unit and
regression tests, and a small number of utility programs used to prepare
input and post-process output. The Plan is limited to these
software components.

\textit{Ludwig} is specifically designed for parallel computers and
relies on the Message Passing Interface \cite{mpi-standard}. The
code will also run in serial, and is designed to be independent of
the platform it is run on. The Plan is therefore not concerned with
hardware or system management activities.

This document is meant to be fairly informal, but will be updated as
the need arises. 
\textit{Ludwig} is an on-going research project, and relies mainly
on funding for the United Kingdom Engineering and Physical Sciences Research
Council to provide support for staff time to work on maintenance and
development. As such, we cannot commit to any and all user requests!

\subsubsection{Definition of key terms}

@@

\textit{Ludwig} is developed by a team based in the School of Physics at
The University of Edinburgh. This involves two groups: the Soft Matter
Physics Group  under the leadership of Prof. Mike Cates FRS, and EPCC in
the person of Kevin Stratford. We collaborate with a number of workers at
different Universities around the world on different aspects of the code.

@@

\subsubsection{Procedures}

There are currently no external constraints on The Plan.

@@

EPCC is responsible for the Software Configuration Management process.
It is anticipated that the cost of this process will be negligible, and
will not require monitoring. There is currently no independent
surveillance of activities to ensure compliance with The Plan.

@@

which is maintained at the Rutherford Appleton Laboratory on behalf
of Collaborative Computational Physics 5 (The Computer Simulation of
Condensed Phases). Subversion identifies different revisions by a
unique revision number. A given version of a file is then uniquely
identified by its path in the repository as it exists at a given
revision number. For example, SVN revision 1416 contains the
following directories:

\texttt{/trunk/doc} source files for this documentation;

\texttt{/trunk/mpi\_s} an MPI stub library;

\texttt{/trunk/src} source code

\texttt{/trunk/targetDP} thread parallelism abstraction layer, currently
under development;

\texttt{/trunk/tests} unit and regression test suite

\texttt{/trunk/util} utility programs

All access is via the CCPForge repository. Users can obtain the code
via anonymous svn access at CPPForge.
All developers of the \textit{Ludwig} project are currently registered with
a CCPForge user account, and fall into one of two categories.
Administrator or Developer. Only the account-holding developers have
permission to change files in the repository. Users have read-only
access.

As CCPForge is not physically under our control, we undertake a
complete dump of the repository itself to a local resource on a
regular basis for security.

@@

Requests for changes or additions to the code should be made via
the issue tracker at CCPForge. The project team will then decide
whether the change is possible. If so, the implementation and
testing of the change will take place, and the new code committed
back to the repository.

@@

Can we account for the status of the code and tests.

\subsubsection{Evaluation and review}

How do we evaluate and audit the code?

\subsubsection{Interface control}

At the moment, we do not explicitly interface to any code outside The
Plan (except MPI). We could extend coverage to include data export
to e.g., Paraview \cite{paraview}.

\subsubsection{Subcontractor / vendor control}

None required.

@@

There is currently no formal release mechanism. If such a mechanism were
introduced, management and  delivery would be via the SVN repository.

\subsection{Schedules}

Sequence of events for SCM process.

\subsection{Resources}

For each active, state what resources (infrastructure, software tools,
personnel etc) are required.

@@

The Plan is currently in a draft form. A complete version of The Plan
will be in place to coincide with the public release.

\newpage
\section{Coordination Meetings}

\begin{thebibliography}{99}
\bibitem{ieee-828-2012} IEEE standard for Configuration Management
\bibitem{mpi-standard} Message passing ineterface.
\bibitem{paraview} Paraview is a standard visualisation package. 
\end{thebibliography}

>>>>

This section contains information on the \textit{Software Configuration
Management Plan} for the \textit{Ludwig} code.
It is to provide users of the code a background on the way in which
the code is developed, how bugs are dealt with, the way in which
new features may be added, how correctness is ensured and tested, and so on.
It is therefore a part
of the process by which the code is maintained. The Software Configuration
Management Plan will be referred to as `The Plan' throughout the remainder
of the section.

@@

The \textit{Ludwig} code is designed to study the hydrodynamic properties
of simple and complex fluids based around the numerical solution of the
Navier-Stokes equations. Complex fluids are dealt with via a free-energy
based finite difference approach, which couples explicitly to the
hydrodynamics.
Components of \textit{Ludwig} include the main program, unit and
regression tests, and a small number support libraries, and a small
number of utility programs used to prepare
input and post-process output. The Plan is limited to these
software components.

\textit{Ludwig} is specifically designed for parallel computers and
relies on the Message Passing Interface \cite{mpi-standard}. The
code will also run in serial, and is independent of
the platform it is run on. The Plan is not concerned with
hardware or system management activities.

\textit{Ludwig} is an on-going research project, and relies mainly
on funding for the United Kingdom Engineering and Physical Sciences Research
Council to provide support for staff time to work on maintenance and
development.

% IEEE section to be completed
%\subsubsection{Definition of key terms}

@@

\textit{Ludwig} is developed by a team based in the School of Physics at
The University of Edinburgh. This involves two groups: the Soft Matter
Physics Group, and Edinburgh Parallel Computing Centre (EPCC). These
groups collaborate with a number of workers at different Universities
around the world on different aspects of the code.

@@

% IEEE section recheck what this actually means
% \subsubsection{Procedures}
% There are currently no external constraints on The Plan.

@@

EPCC is responsible for the Software Configuration Management process.
It is anticipated that the cost of this process will be small as the
project team can communicate informally on a regular basis. There is
currently no independent
surveillance of activities to ensure compliance with The Plan.

@@

which is maintained at the Rutherford Appleton Laboratory on behalf
of Collaborative Computational Physics 5 (The Computer Simulation of
Condensed Phases). Subversion identifies different revisions by a
unique revision number. A given version of a file is then uniquely
identified by its path in the repository as it exists at a given
revision number.

% Add pointer to standard manifest (README)

All access to the code is via the CCPForge repository. CCPForge identifies
three different levels of access:

\textit{Administrators:} allows administration of the site itself and
registered members;

\textit{Developers:} members who have write access to the source code repository;

\textit{Users:} have read only access to the source code via SVN (either
as a member or via anonymous download). Member users also have access to
the tracker.

As CCPForge is not physically under the control of EPCC, a
complete dump of the repository to a local resource is undertaken on a
regular basis for security.

@@

Requests for changes or additions to the code should be made via
the issue tracker at CCPForge. The project team will then decide
whether the change is possible and/or desirable. If so, the
implementation and testing of the change will take place, and the
new code committed back to the repository.

\textit{Submitting a change request:} A description of the proposed change
will be submitted to the CCPForge issue tracker as a change request to
provide a record of the change process.

\textit{Evaluating a change request:} The request, together with any
additional information, will be evaluated by the SCM team. The request
will be accepted, refined, or rejected as appropriate. The change owner
will make necessary updates to the change record.

\textit{Implementation of change:} Important changes to behaviour of code
related to a change will be
accompanied by a relevant descriptive record in the change request.

\textit{Version control:} A \texttt{MAJOR.MINOR.PATCH} numerical version
name scheme is used \cite{apacheAPR}.
It is expected that bug fixes and relatively
small changes will be accompanied by a unit increment in the patch level;
more significant changes will be reflected at the minor version number;
major reconstructions will occur rarely and incur a change of major version
number.

@@

% Privides tracability of changes, pending completed, etc
% Configuration reports, release notes

The status of changes will be tracked at the CCPForge issue tracker
with a named SCM team member owning the change. The relevant tracker
item will be closed when successfully implemented and tested.

The tracker is available to CPPForge member users to provide a record
of changes to the code. Anonymous users will be alerted to changes via
release notes.

%\subsubsection{Evaluation and review}
%There are currently no formal mechna audit the code?

% \subsubsection{Interface control}
% This section discusses other organisations the developers must
% ``interface'' with.

% IEEE section not relevant
%\subsubsection{Subcontractor / vendor control}

@@

There are currently no formal releases of the \textit{Ludwig} code.
Any release management and  delivery will be via the SVN repository.

% IEEE section. We don't really have any schedules.
%\subsection{Schedules}

%\subsection{Resources}

% Software resources (dependencies, etc)
% Hardware resources
% Human resources

@@

The Plan is currently under review to consider organisational changes
affecting the responsibilities different stakeholders.

%\newpage
%\section{Coordination Meetings}

\begin{thebibliography}{99}
\bibitem{ieee-828-2012} IEEE Standard 828-2011 ``IEEE Standard for
Software Configuration Management Plans''
\bibitem{mpi-standard} Message Passing Interface Forum. MPI: A Message
Passing Interface Standard Version 1.3 (1998).
%\bibitem{paraview} Paraview is a standard visualisation package. 
\bibitem{apacheAPR} See, e.g., the Apache Portable Runtime Project ``APR's Version Numbering''  https://apr.apache.org/versioning.html (Accessed 2015).
\end{thebibliography}

\vfill\eject
